### 2020-06-30 paper/sex_selection_spacing-ver4.tex
Edit for clarity and include summary of results in spacing section

\subsection{Interpretation}

To what extent has the introduction of sex selection changed birth spacing across sex 
compositions?
There are three broad groups in the data.

First, women who have only girls but do not use sex selection had, and continue to have,
the shortest spacing, as shown, for example, by rural women with no education.
For this group, spacing is shortest with only girls across all spell, and the difference
between sex compositions have even grown over time.

[TK this is not clear]
Second, even with sex selection and the associated increases in expected spacing, the
intervals for the other sex compositions have increased even more, and the relative 
pattern, therefore, remains more or less the same.
An example is for the second spell for women with eight to eleven
and twelve or more years of education.

Finally, women with the most biased sex ratios have the longest spacing in the 
absence of boys, and this spacing is longer than for the other possible sex 
compositions.
The most extreme example is that with a sex ratio for the best-educated urban women  
approaching 80 percent, the 42 months birth intervals with two girls is seven months 
longer than with at least one boy.
However, even urban women with eight to eleven years of education show the longest 
intervals with only girls in the last period.

>>>>

\subsection{Sex Selection and Birth Spacing}

The results above show that average birth intervals increased over time across all groups 
and that these increases are larger for higher parities and with more schooling. 
Furthermore, the increases come predominately from the longer intervals getting even 
longer while there is little change in the length of the shortest intervals.

What do these results tell us about the extent to which the introduction of sex selection 
changed birth spacing across sex compositions? 
There are three broad groups in the data.

The first group consists of women who do not use sex selection even if they have only 
girls, such as rural women with no education. 
For this group, the shortest spacing---across all spells---is when they have only girls. 
Notably, the difference in birth intervals across sex compositions has even grown over 
time as spacing when sons are present increased.

In the second group are women who use sex selection and who, therefore, show the expected 
associated increase in birth intervals for those sex compositions. 
However, the intervals for their other sex compositions have increased even more. 
The result is that the relative pattern remains more or less the same. 
An example of this group is women with eight more years of education in the second spell.

The final group consists of those women, who, in the absence of a son, have the most 
biased sex ratios and the longest birth intervals, and where this spacing is longer than 
for the other possible sex compositions. 
The most extreme example is best-educated urban women with two girls with a sex ratio 
approaching 80 and an average birth interval of 42 months. 
This birth interval is seven months longer than with at least one boy.

In summary, although birth spacing has increased over time with improving economic 
conditions and falling fertility, it is clear that most of the increases in birth spacing 
come from the increased use of sex selection. 
The most substantial increase over the four decades is a full year for the best-educated 
women with two girls.
